Usage metrics

### 2020-12-18 analysis/usage.Rmd
Percent of symbols coming from ggplot

@@

overview_table(
  r("Symbolpercent", ratio(symbs, nb_calls)),
  r("Languagepercent", ratio(languages, nb_calls)),
  r("Expressionpercent", ratio(expressions, nb_calls)),
  r("Codepercent", ratio(symbs + languages + expressions, nb_calls))
) -> TBL
```

>>>>

# Diversity of arguments

@@

ggplot2_symbs <- E %>% filter(ev_package == "ggplot2") %>% count(type, wt=duplicates) %>% filter(type == "symbol") %>% .$n

overview_table(
  r("Symbolpercent", ratio(symbs, nb_calls)),
  r("Languagepercent", ratio(languages, nb_calls)),
  r("Expressionpercent", ratio(expressions, nb_calls)),
  r("Codepercent", ratio(symbs + languages + expressions, nb_calls)),
  r("Ggplotsymbolpercent", ratio(ggplot2_symbs, symbs))
) -> TBL
```
